Fusion Moves for Correlation Clustering

### 2014-11-09 paper/anytimefigure2.tex
new figures, new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}
    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};

@@

  \begin{semilogxaxis}[

@@

  legend to name = named,

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{named}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}
    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};

@@

  \begin{semilogxaxis}[  mark size=1pt,

@@

  legend to name = ledgendPosition,

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPosition}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    FOO
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-09 paper/egpaper_for_review.tex
new figures, new stuff

@@

@@

\textbf{Desired Properties}

@@

\subsubsection{Randomized MaxCut  (RMC)}

To get energy aware proposals we can use max cuts.
The max cut objective is the same as
the multicut objective, but only two 
node colors are allowed.
Therefore solutions of the max cut objective
might be useful proposals.
To create different proposals we set 
the weight of edges which are cut 
in the best solution to zero.
In this way we favor solutions 
different form the current best. 
In addition we either add noise permute a certain number of weights.

@@

\input{inputs/fig_hc.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4600,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  ]
  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
  %\addlegendentry{CGC-planar}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
    restrict y to domain=-6000:-4500,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    %ymin =  75282844.25,
    %ymax =  81774642.015,
    %xtick       = { 1 , 60 , 3600 },
    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
    %ytick       = {75661636, 78718140, 81774643 },
    %yticklabels = {$75661636$, $78718140$, $81774643$ },
    width = 1.0\columnwidth,
    scaled ticks = false
    ]
    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
    %%\addlegendentry{HC-CGC}
    %
    \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
    %\addlegendentry{CGC} 
    %
    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
    %\addlegendentry{MCI-CCIFD} 
    %
    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
    %\addlegendentry{MC-Fusion (HC-MC-CGC)}
    %
    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
    %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
    %
    \end{semilogxaxis}
    \end{tikzpicture}
    \caption{knott-3d-150}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-40000:-24000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  legend to name = named,
  legend columns=5
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
  \addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-300.data};
  \addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-300.data};
  \addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-300.data};
  \addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-300.data};
  \addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-300}
  \end{subfigure}
  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-80000:-60000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-450}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-10000000:-100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
  %\addlegendentry{MCI-CCIFD}

  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}

  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-550}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  restrict y to domain=-10000000:700000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
  %\addlegendentry{CGC}

  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
  %\addlegendentry{MCI-CCIFD}

  %\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
  %%\addlegendentry{MC-Fusion (HC-MC)}

  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
  %DYNCC-HC-CGC-CGC
  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{seg-3d}
  \end{subfigure}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{named}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{anytimefigure.tex}

>>>>

\input{inputs/fig_notation.tex}

@@

\input{inputs/fig_contraction.tex}

@@

\noindent \textbf{Desired Properties:}
As discussed in \cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
The quality / energy of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
Diversity between the individual proposals
reduces the chances to get stuck in local minima.
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).

@@

%\subsubsection{Randomized MaxCut  (RMC)}
%
%To get energy aware proposals we can use max cuts.
%The max cut objective is the same as
%the multicut objective, but only two 
%node colors are allowed.
%Therefore solutions of the max cut objective
%might be useful proposals.
%To create different proposals we set 
%the weight of edges which are cut 
%in the best solution to zero.
%In this way we favor solutions 
%different form the current best. 
%In addition we either add noise permute a certain number of weights.

@@

%\input{inputs/fig_hc.tex}

@@
